Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-03-02 paper.tex
added reference
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Models are largely employed in the science and engineering areas, in order to analyze, predict and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many engineering advances, in the last centuries. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions. Nonetheless, one can argue that such models are not enough to represent CPSs, because the interaction among software, communications, and hardware presents a lot of events that could not be deterministically or stochastically modeled and may be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, the early representation of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in representing discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which may even be negligible. On the other hand, that approach is not suitable for complex CPSs that present a lot of nondeterminism, given that uncertainties play a central role.

@@

There are several invariant-generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also discover the memory ``shape'', in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems, using invariant generation and strengthening, mostly based on interval analysis. \textcolor{red}{eh bom citar essa literatura aqui}

>>>>

Models are largely employed in the science and engineering areas, in order to analyze, predict, and modify the behavior of real-world systems. Specially, deterministic and stochastic models are the basis of many engineering advances, in the last centuries. The former is uniquely determined by parameter values and previous states, while the latter presents inherent randomness, which is described by probability distributions. Nonetheless, one can argue that such models are not enough to represent CPS since the interaction among software, communications, and hardware presents a lot of events that could not be deterministically or stochastically modeled and may be better represented by nondeterministic approaches~\cite{leeCPS2}. Indeed, that is even more evident when unknown properties are addressed, such as human behavior.

On the one hand, the early representation of hybrid systems, {\it i.e.}, systems that mix continuous and discrete dynamics, consisted in representing discrete components and discretized continuous dynamics by using discrete models and considering non-modeled effects as uncertainties or perturbations exogenous to them, which may even be negligible. On the other hand, that approach is not suitable for complex CPS that present intense nondeterminism, given that uncertainties play a central role.

@@

There are several invariant-generation algorithms that discover linear and polynomial relations among integer and real variables, in order to provide loop invariants and also discover the memory ``shape'', in programming languages with pointers~\cite{pips:2013,Henry:2012}. The current literature also reports successful applications of \textit{k}-induction based verification algorithms for hardware and software systems, using invariant generation and strengthening, mostly based on interval analysis~\cite{Beyer15}.
